---
title: 'Full Code: Decoding Airbnb in The Big Apple'
author: 'Daksh Goyal, Nitin Kumar, Sai Krishna Lanka, Wen Luo'
date: '6/22/2020'
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load libraries and set options}
if(!require('pacman')) install.packages('pacman')
pacman::p_load(
  tidyverse,
  plotly,
  RColorBrewer,
  broom,
  sp,
  rgdal,
  sf,
  tmap,
  forecast,
  gains,
  shiny,
  leaflet,
  textstem,
  tm,
  wordcloud,
  reshape2,
  rgeos,
  DT)

theme_set(theme_classic())

tmap_mode('view')
```

```{r load data}
listing.df <- read_csv('../data/listings_clean.csv', col_types = cols())
review.df <- read_csv('../data/reviews_clean.csv', col_types = cols())
calendar.df <- read_csv('../data/calendar_clean.csv', col_types = cols())

borough.geo.df <- read_sf('../data/Borough Boundaries.geojson', quiet = TRUE)
borough.geo <- readOGR('../data/Borough Boundaries.geojson', verbose = FALSE)
hood.geo <- readOGR(dsn = '../data/NTA Boundaries.geojson', verbose = FALSE)
```

### How has Airbnb presence grown over the years?

```{r}
listyear.fields <- c('host_since', 'neighbourhood_group_cleansed','property_type','longitude', 'latitude')
listyear.df <- na.omit(listing.df[, listyear.fields])

listyear.df$host_since_year <- format(listyear.df$host_since, '%Y')
listyear.df$property_type <- as.factor(listyear.df$property_type)
listyear.df$longitude <- as.numeric(listyear.df$longitude)
listyear.df$latitude <- as.numeric(listyear.df$latitude)
```

```{r}
data.frame(table(format(listing.df$host_since, '%Y'))) %>%
  plot_ly(type = 'bar', x = ~Var1, y = ~Freq, hoverinfo = 'text', 
          text = ~paste('Year: ', Var1, ', Count: ', Freq)) %>%
  layout(title = 'Barplot: New Listings per Year', 
         xaxis = list(title = 'Year'), 
         yaxis = list(title = '# of Listings'))
```

```{r}
accumulate_by <- function(dat, var) {
  var <- lazyeval::f_eval(var, dat)
  lvls <- plotly:::getLevels(var)
  dats <- lapply(seq_along(lvls), function(x) {
    cbind(dat[var %in% lvls[seq(1, x)], ], frame = lvls[[x]])
  })
  dplyr::bind_rows(dats)
}

ggplotly(ggplot(borough.geo.df) + geom_sf() + ggtitle('Growth of Airbnb in NYC') +
           theme(plot.title = element_text(hjust = 0.5))) %>%
  add_trace(type = 'scatter', mode = 'markers', y = ~latitude, x = ~longitude, frame = ~frame,
            data = listyear.df %>% accumulate_by(~host_since_year),
            marker = list(color = 'firebrick', size = 2), hoverinfo = 'text',
            text = ~property_type, showlegend = F) %>%
  animation_slider(currentvalue = list(prefix = 'Year: ', font = list(color = 'firebrick')))

# listyear.gif <- 
#   tm_shape(borough.geo) +
#   tm_borders(col = 'grey40', lwd = 2) + 
#   tm_shape(st_as_sf(x = listyear.df %>% 
#                       accumulate_by(~host_since_year), 
#                     coords = c('longitude', 'latitude'), 
#                     crs = proj4string(borough.geo))) +
#   tm_dots(col = 'firebrick4', size = 0.1) +
#   tm_facets(by = 'frame', free.coords = FALSE) +
#   tm_layout(title = 'Growth of NYC')
# 
# tmap_animation(listyear.gif, filename = '../support/airbnb_growth.gif', delay = 200, width = 1000)
```

### How costly are the Airbnb rates in the neighbourhoods across the five boroughs?

```{r}
pricehood.fields <- c('neighbourhood_cleansed', 'neighbourhood_group_cleansed', 'price', 'guests_included')
pricehood.df <- na.omit(listing.df[, pricehood.fields])

pricehood.df$neighbourhood_cleansed <- as.factor(pricehood.df$neighbourhood_cleansed)
pricehood.df$neighbourhood_group_cleansed <- as.factor(pricehood.df$neighbourhood_group_cleansed)
pricehood.df$price <- as.numeric(pricehood.df$price)
pricehood.df$guests_included <- as.integer(pricehood.df$guests_included)
```

```{r}
pricehood.df %>% 
  plot_ly(type = 'box', y = ~round(price/guests_included, 2), color = ~neighbourhood_group_cleansed,
          colors = 'Dark2') %>% 
  layout(title = 'Boxplot: Rate per One Guest w.r.t. Borough', 
         yaxis = list(title = 'Rate per One Guest'))

pricehood.df %>% 
  plot_ly(type = 'box', y = ~round(log(price/guests_included), 2), color = ~neighbourhood_group_cleansed,
          colors = 'Dark2') %>% 
  layout(title = 'Boxplot: Log of Rate per One Guest w.r.t. Borough', 
         yaxis = list(title = 'Log of Rate per One Guest'))
```

```{r}
medianpricehood.df <- pricehood.df %>% 
  group_by(neighbourhood_group_cleansed, neighbourhood_cleansed) %>% 
  summarise(count = n(), median_price_per_guest = round(median(price/guests_included), 2))

medianpricehood.df[medianpricehood.df$count < 5, ]$median_price_per_guest <- NA

medianpricehood.geo <- hood.geo
medianpricehood.geo@data <- left_join(hood.geo@data, medianpricehood.df, 
                                      by = c('neighbourhood' = 'neighbourhood_cleansed'))

medianpricehood.geo$text <- paste0('Neighbourhood:', medianpricehood.geo$neighbourhood, 
                                   ' | Count:' , medianpricehood.geo$count,
                                   ' | Median Rate per Guest: $', 
                                   medianpricehood.geo$median_price_per_guest)
```

```{r}
tm_shape(medianpricehood.geo) +
  tm_fill(col = 'median_price_per_guest', palette = 'Reds', alpha = 0.7, n = 10,
          title = 'Median Rate per Guest (in $)', id = 'text') +
  tm_borders(col = 'grey60', lwd = 1) + 
  tm_shape(borough.geo) +
  tm_borders(col = 'grey40', lwd = 2) + 
  tm_text(text = 'boro_name', size = 1, col = 'black') +
  tm_layout(title = 'NYC: Rate for 1-Night')
```

```{r}
medianpricehood.df %>% 
  filter(neighbourhood_group_cleansed == 'Manhattan') %>% 
  arrange(desc(median_price_per_guest)) %>% 
  top_n(5, median_price_per_guest)

medianpricehood.df %>% 
  filter(neighbourhood_group_cleansed == 'Brooklyn') %>% 
  arrange(desc(median_price_per_guest)) %>% 
  top_n(5, median_price_per_guest)
```

### How badly the Covid-19 crisis affect Airbnb?

```{r}
calendar.df$date <- as.Date(calendar.df$date, format = '%Y-%m-%d')
calendar.df <- calendar.df[which(calendar.df$date >= '2020-05-15' & calendar.df$date <= '2020-07-15'), 
                           c('listing_id', 'date', 'adjusted_price')]
calendar.df$adjusted_price <- as.numeric(gsub('[^0-9.]', '', as.character(calendar.df$adjusted_price)))

calendar.df <- calendar.df %>% 
  inner_join(listing.df[, c('id', 'neighbourhood_group_cleansed', 'guests_included')], 
             by = c('listing_id' = 'id')) %>%
  group_by(neighbourhood_group_cleansed, date)
```

```{r}
calendar.df %>%
  summarise(mean_price = round(mean(adjusted_price/guests_included, na.rm = TRUE), 2)) %>%
  plot_ly(type = 'scatter', mode = 'lines', x = ~date, y = ~mean_price,  
          color = ~neighbourhood_group_cleansed, colors = 'Dark2') %>% 
  layout(title = 'Trendplot: Mean Rates per Guest for Various Boroughs 
         from May 15, 2020 to Jul 15, 2020', 
         xaxis = list(title = 'Time'),
         yaxis = list(title = 'Mean Price'),
         legend = list(orientation = 'h', xanchor = 'center', x = 0.5, y = -0.2))

calendar.df %>%
  mutate(price_guest = log(adjusted_price/guests_included), weekday = weekdays(date)) %>%
  mutate(weekday = factor(weekday, levels = c('Monday', 'Tuesday', 'Wednesday', 'Thursday',
                                              'Friday', 'Saturday', 'Sunday'))) %>%
  plot_ly(type = 'box', y = ~price_guest, x = ~neighbourhood_group_cleansed, color = ~weekday,
          colors = 'Dark2') %>%
  layout(title = 'Boxplot: Log of Rates for Weekdays for Various Boroughs
         from May 15, 2020 to Jul 15, 2020',
         xaxis = list(title = 'Boroughs'),
         yaxis = list(title = 'Log of Rates per 1 Night'),
         boxmode = 'group')
```

### What should be the rental value if you want to list your property with Airbnb?

```{r}
rate.fields <- c('neighbourhood_group_cleansed', 'neighbourhood_cleansed', 'property_type', 'room_type', 
                 'bedrooms', 'bathrooms', 'guests_included', 'price')
rate.df <- na.omit(listing.df[, rate.fields])

rate.df$neighbourhood_group_cleansed <- as.factor(rate.df$neighbourhood_group_cleansed)
rate.df$neighbourhood_cleansed <- as.factor(rate.df$neighbourhood_cleansed)
rate.df$property_type <- as.factor(rate.df$property_type)
rate.df$room_type <- as.factor(rate.df$room_type)
rate.df$bedrooms <- as.integer(rate.df$bedrooms)
rate.df$bathrooms <- as.numeric(rate.df$bathrooms)
rate.df$guests_included <- as.integer(rate.df$guests_included)
rate.df$price <- as.numeric(rate.df$price)

rate.df <- rate.df[!apply(rate.df[, c('price')], 1, function(x) any(x == 0)), ]
```

```{r}
rate.df %>% 
  plot_ly(type = 'histogram', x = ~price) %>%
  layout(title = 'Histogram: Rate per 1-Night', 
         xaxis = list(title = 'Rate (in $)'), yaxis = list(title = '# of Listings'))
```

```{r}
rate.df$lnprice <- log(rate.df$price)

rate.df %>% 
  plot_ly(type = 'histogram', x = ~lnprice, nbinsx = 50) %>%
  layout(title = 'Histogram: Log of Rate per 1-Night', 
         xaxis = list(title = 'Log of Rate'), yaxis = list(title = '# of Listings'))
```

```{r}
lnprice.lq <- quantile(rate.df$lnprice, probs = 0.25)
lnprice.uq <- quantile(rate.df$lnprice, probs = 0.75)
lnprice.iqr <- 1.5 * (lnprice.uq - lnprice.lq)
rate.df <- rate.df[between(rate.df$lnprice, lnprice.lq - lnprice.iqr, lnprice.uq + lnprice.iqr), ]

rate.df <- rate.df[rate.df$neighbourhood_cleansed %in% 
                     names(which(table(rate.df$neighbourhood_cleansed) >= 5)), ]
rate.df$neighbourhood_cleansed <- as.factor(as.character(rate.df$neighbourhood_cleansed))

rate.df <- rate.df[rate.df$property_type %in% 
                     names(which(table(rate.df$property_type) >= 100)), ]
rate.df$property_type <- as.factor(as.character(rate.df$property_type))
```

```{r}
rate.df %>%
  plot_ly(type = 'histogram', x = ~lnprice, nbinsx = 30) %>%
  layout(title = 'Histogram: Log of Rate per 1-Night without Outliers',
         xaxis = list(title = 'Log of Rate'), yaxis = list(title = '# of Listings'))
```

```{r}
rate.df %>% 
  filter(neighbourhood_group_cleansed == 'Manhattan') %>% 
  plot_ly(type = 'box', y = ~lnprice, color = ~neighbourhood_cleansed, 
          colors = colorRampPalette(brewer.pal(n = 8, name = 'Dark2'))(50)) %>% 
  layout(title = 'Boxplot: Log of Rates for Various Neighbourhoods in Manhattan', 
         yaxis = list(title = 'Log of Rates per 1 Night'))

rate.df %>% 
  filter(neighbourhood_group_cleansed == 'Brooklyn') %>% 
  plot_ly(type = 'box', y = ~lnprice, color = ~neighbourhood_cleansed, 
          colors = colorRampPalette(brewer.pal(n = 8, name = 'Dark2'))(50)) %>% 
  layout(title = 'Boxplot: Log of Rates for Various Neighbourhoods in Brooklyn', 
         yaxis = list(title = 'Log of Rates per 1 Night'))

rate.df %>% 
  filter(neighbourhood_group_cleansed == 'Bronx') %>% 
  plot_ly(type = 'box', y = ~lnprice, color = ~neighbourhood_cleansed, 
          colors = colorRampPalette(brewer.pal(n = 8, name = 'Dark2'))(50)) %>% 
  layout(title = 'Boxplot: Log of Rates for Various Neighbourhoods in Bronx', 
         yaxis = list(title = 'Log of Rates per 1 Night'))

rate.df %>% 
  filter(neighbourhood_group_cleansed == 'Queens') %>% 
  plot_ly(type = 'box', y = ~lnprice, color = ~neighbourhood_cleansed, 
          colors = colorRampPalette(brewer.pal(n = 8, name = 'Dark2'))(50)) %>% 
  layout(title = 'Boxplot: Log of Rates for Various Neighbourhoods in Queens', 
         yaxis = list(title = 'Log of Rates per 1 Night'))

rate.df %>% 
  filter(neighbourhood_group_cleansed == 'Staten Island') %>% 
  plot_ly(type = 'box', y = ~lnprice, color = ~neighbourhood_cleansed, 
          colors = colorRampPalette(brewer.pal(n = 8, name = 'Dark2'))(10)) %>% 
  layout(title = 'Boxplot: Log of Rates for Various Neighbourhoods in Staten Island', 
         yaxis = list(title = 'Log of Rates per 1 Night'))
```

```{r}
rate.df %>%
  plot_ly(type = 'box', y = ~lnprice, color = ~property_type, 
          colors = colorRampPalette(brewer.pal(n = 8, name = 'Dark2'))(50)) %>% 
  layout(title = 'Boxplot: Log of Rates for Various Property Types', 
         yaxis = list(title = 'Log of Rates per 1 Night'))

rate.df %>% 
  plot_ly(type = 'box', y = ~lnprice, color = ~room_type, colors = 'Dark2') %>% 
  layout(title = 'Boxplot: Log of Rates for Various Room Types', 
         yaxis = list(title = 'Log of Rates per 1 Night'))

```

```{r}
rate.df$neighbourhood_group_cleansed <- relevel(rate.df$neighbourhood_group_cleansed, 'Manhattan')
rate.df$neighbourhood_cleansed <- relevel(rate.df$neighbourhood_cleansed, 'Harlem')
rate.df$property_type <- relevel(rate.df$property_type, 'Apartment')
rate.df$room_type <- relevel(rate.df$room_type, 'Entire home/apt')

set.seed(1)
train.index <- sample(c(1:dim(rate.df)[1]), dim(rate.df)[1]*0.7)
```

```{r}
rate.linr1 <- lm(lnprice ~ neighbourhood_group_cleansed + property_type + room_type + bedrooms + 
                   bathrooms + guests_included, 
                 data = rate.df, subset = train.index, na.action = na.exclude)
glance(rate.linr1) %>%
  dplyr::select(r.squared, adj.r.squared, AIC, BIC)

rate.linr2 <- lm(lnprice ~ neighbourhood_cleansed + property_type + room_type + bedrooms + 
                   bathrooms  + guests_included, 
                 data = rate.df, subset = train.index, na.action = na.exclude)
glance(rate.linr2) %>%
  dplyr::select(r.squared, adj.r.squared, AIC, BIC)
```

```{r}
rate.linr3 <- step(lm(lnprice ~ 1, data = rate.df, subset = train.index, na.action = na.exclude),
                   scope = list(lower = lnprice ~ 1, upper = formula(rate.linr2)),
                   direction = 'forward', trace = 0,  k = log(nrow(rate.df[train.index, ])))
formula(rate.linr3)

rate.linr4 <- step(rate.linr2, scope = list(lower = lnprice ~ 1, upper = formula(rate.linr2)),
                   direction = 'backward', trace = 0,  k = log(nrow(rate.df[train.index, ])))
formula(rate.linr4)
```

```{r}
rate.linr.pred.train <- predict(rate.linr2, na.action = na.pass)
accuracy(rate.linr.pred.train, rate.df[train.index, ]$lnprice)

rate.linr.pred.valid <- predict(rate.linr2, newdata = rate.df[-train.index, ], na.action = na.pass)
accuracy(rate.linr.pred.valid, rate.df[-train.index, ]$lnprice)

rate.predict.valid.df <- data.frame(rate.df[-train.index, !(names(rate.df) %in% c('price', 'lnprice'))], 
                                    actual_rate = rate.df[-train.index, ]$price, 
                                    prediced_rate = round(exp(rate.linr.pred.valid), 2))
```

```{r}
rate.linr <- lm(lnprice ~ neighbourhood_cleansed + property_type + room_type + bedrooms + 
                   bathrooms  + guests_included, 
                 data = rate.df, na.action = na.exclude)

predict.ui <- fluidPage(
  tags$style('body {
      -moz-transform: scale(0.8, 0.8); /* Moz-browsers */
      zoom: 0.8; /* Other non-webkit browsers */
      zoom: 80%; /* Webkit browsers */}'),
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = 'borough', label = 'Borough: ',
                  choices = sort(levels(rate.df$neighbourhood_group_cleansed)), selected = 'Manhattan'),
      uiOutput('bhood'),
      selectInput(inputId = 'prop', label = 'Property Type: ', 
                  choices = sort(levels(rate.df$property_type)), selected = 'Apartment'),
      uiOutput('proprm'),
      selectInput(inputId = 'bed', label = 'Number of Bedrooms: ', 
                  choices = seq(0, 10, 1), selected = 1),
      selectInput(inputId = 'bath', label = 'Number of Bathrooms: ',
                  choices = seq(1.0, 7.0, 0.5), selected = 1),
      selectInput(inputId = 'guest', label = 'Number of Guests Included: ',
                  choices = seq(1, 15, 1), selected = 1)
    ),
    mainPanel(leafletOutput(outputId= 'map', width = '100%', height = '600')
    )
  )
)


predict.server <- function(input, output) {
  
  output$bhood <- renderUI({
    selectInput(inputId = 'hood', label = 'Neighbourhood: ', 
                choices = rate.df %>%
                  filter(neighbourhood_group_cleansed == input$borough) %>%
                  select(neighbourhood_cleansed) %>%
                  unique() %>%
                  arrange(neighbourhood_cleansed),
                selected = 'Harlem')
  })
  
  output$proprm <- renderUI({
    selectInput(inputId = 'room', label = 'Room Type: ', 
                choices = rate.df %>%
                  filter(property_type == input$prop) %>%
                  select(room_type) %>%
                  unique() %>%
                  arrange(room_type),
                selected = 'Entire home/apt')
  })
  
  output$map <- renderLeaflet({
    res.df <- data.frame('neighbourhood_cleansed' = input$hood, 
                         'property_type' = input$prop,
                         'room_type' = input$room, 
                         'bedrooms' = as.integer(input$bed),
                         'bathrooms' = as.numeric(input$bath), 
                         'guests_included' = as.integer(input$guest))
    res.pred.df <- predict(rate.linr, newdata = res.df, na.action = na.pass, interval = 'prediction')
    res.pred.df <- round(exp(res.pred.df), 2)
    res.df <- cbind(res.df, res.pred.df)
    res.df$text <- paste0('Rate: $', res.df$fit, ' | Lower 2.5%: $', res.df$lwr, 
                          ' | Upper 97.5%: $' , res.df$upr)
    res.geo <- hood.geo[hood.geo$neighbourhood == input$hood, ]
    res.geo <- merge(res.geo, res.df, by.x = 'neighbourhood', by.y = 'neighbourhood_cleansed')
    tmap_leaflet(tm_shape(res.geo) +
                   tm_fill(id = 'neighbourhood', col = 'darkseagreen', alpha = 0.7, n = 6) +
                   tm_borders() + 
                   tm_text(text = 'text', size = 1.5, col = 'black') +
                   tm_layout(title = paste0('Predicted Rate (1-Night) for Airbnb rentals in ',
                                            res.geo$neighbourhood)))
  })
  
}


shinyApp(ui = predict.ui, server = predict.server)
```

### What are the pain points that a guest finds in Airbnb?

```{r}
data.frame(prop.table(table(listing.df$review_scores_rating))*100) %>%
  plot_ly(type = 'bar', x = ~Var1, y = ~Freq, hoverinfo = 'text', 
          text = ~paste('Rating: ', Var1, ', Percentage: ', round(Freq, 2))) %>%
  layout(title = 'Barplot: Ratings vs % of Listings', 
         xaxis = list(title = 'Rating'), 
         yaxis = list(title = '% of Listings'))
```

```{r}
clean_string <- function(string){
  temp <- tolower(string)
  temp <- str_replace_all(temp,"[^a-zA-Z'\\s]", " ")
  temp <- str_replace_all(temp, "[\\s]+", " ")
  temp <- str_trim(temp, side = 'both')
  return(temp)
}

nlp_clean_string <- function(string){
  temp <- lemmatize_strings(string)
  temp <- str_replace_all(temp, "n't", " not")
  corpus <- Corpus(VectorSource(temp), readerControl = list(language = 'en'))
  corpus <- tm_map(corpus, removeWords, c(stopwords('en')))
  # corpus <- tm_map(corpus, stripWhitespace)
  temp <- corpus[[1]]$content
  return(temp)
}

review.df$comments <-sapply(review.df$comments, clean_string)
review.df$comments <-sapply(review.df$comments, nlp_clean_string)

words <- Corpus(VectorSource(review.df$comments), readerControl = list(language = 'en')) %>%
  DocumentTermMatrix(control = list(weighting = weightTfIdf)) %>%
  as.matrix() %>%
  colSums() %>%
  sort(decreasing = TRUE)

set.seed(42)
wordcloud(words = names(words), freq = words, min.freq = 1, max.words = 200,
          random.order = FALSE, rot.per = 0.35, colors = brewer.pal(8, 'Dark2'))
```

### What are the top 10 listing recommendations based on customer constraints?

```{r}
recommend.fields <- c('listing_url', 'neighbourhood_group_cleansed', 'neighbourhood_cleansed', 'latitude', 
                      'longitude', 'property_type', 'room_type', 'bedrooms', 'bathrooms', 'guests_included',
                      'price')
recommend.df <- na.omit(listing.df[, recommend.fields])

recommend.df$listing_url <- as.character(recommend.df$listing_url)
recommend.df$listing_url <- paste0('<a target = "_blank", href="', recommend.df$listing_url, '">', 
                                   recommend.df$listing_url, '</a>')
recommend.df$neighbourhood_cleansed <- as.factor(recommend.df$neighbourhood_cleansed)
recommend.df$neighbourhood_group_cleansed <- as.factor(recommend.df$neighbourhood_group_cleansed)
recommend.df$latitude <- as.numeric(recommend.df$latitude)
recommend.df$longitude <- as.numeric(recommend.df$longitude)
recommend.df$property_type <- as.factor(recommend.df$property_type)
recommend.df$room_type <- as.factor(recommend.df$room_type)
recommend.df$bedrooms <- as.integer(recommend.df$bedrooms)
recommend.df$bathrooms <- as.numeric(recommend.df$bathrooms)
recommend.df$guests_included <- as.integer(gsub('[^0-9.]', '', as.character(recommend.df$guests_included)))
recommend.df$price <- as.numeric(gsub('[^0-9.]', '', as.character(recommend.df$price)))
recommend.df$price_guest <- round(recommend.df$price/recommend.df$guests_included, 2)
```

```{r}
recommend.ui <- fluidPage(
  tags$style('body {
      -moz-transform: scale(0.8, 0.8); /* Moz-browsers */
      zoom: 0.8; /* Other non-webkit browsers */
      zoom: 80%; /* Webkit browsers */}'),
  tags$style(HTML('table.dataTable tr.selected td, 
                  table.dataTable td.selected {background-color: #fff !important;}')),
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = 'borough', label = 'Borough: ',
                  choices = sort(levels(recommend.df$neighbourhood_group_cleansed)), 
                  selected = 'Manhattan'),
      uiOutput('bhood'),
      selectInput(inputId = 'bed', label = 'Number of Bedrooms: ', 
                  choices = seq(0, 10, 1), selected = 1),
      selectInput(inputId = 'guest', label = 'Number of Guests Included: ',
                  choices = seq(1, 15, 1), selected = 1),
      numericInput(inputId = 'price', label = 'Budget : ',
                   value = 50, min = 1, max = 10000),
      width = 5
    ),
    mainPanel(
      leafletOutput(outputId= 'map', width = '100%', height = '500'),
      width = 7
    )
  ),
  dataTableOutput(outputId = 'recdf', width = '100%', height = '500')
)


recommend.server <- function(input, output) {
  
  output$bhood <- renderUI({
    selectInput(inputId = 'hood', label = 'Neighbourhood: ', 
                choices = recommend.df %>%
                  filter(neighbourhood_group_cleansed == input$borough) %>%
                  select(neighbourhood_cleansed) %>%
                  unique() %>%
                  arrange(neighbourhood_cleansed), 
                selected = 'Harlem')
  })  
  
  recommend.geo <- reactive({
    recommend.geo <- recommend.df %>% filter(neighbourhood_group_cleansed == input$borough)
    coordinates(recommend.geo) <- ~longitude+latitude
    
    search.pt <- coordinates(hood.geo[hood.geo$neighbourhood == input$hood, ])
    search.pt.geo <- data.frame('listing_url' = NA,
                                'neighbourhood_group_cleansed' = input$borough,
                                'neighbourhood_cleansed' = input$hood,
                                'longitude' = search.pt[1], 'latitude' = search.pt[2],
                                'property_type' = NA, 'room_type' = NA, 
                                'bedrooms' = as.integer(input$bed), 'bathrooms' = NA,
                                'guests_included' = as.integer(input$guest),
                                'price' = as.numeric(input$price),
                                'price_guest' = as.numeric(input$price)/as.integer(input$guest))
    coordinates(search.pt.geo) <- ~longitude+latitude
    
    recommend.geo$rank <- rank(gDistance(search.pt.geo, recommend.geo, byid = TRUE))
    recommend.geo <- recommend.geo[recommend.geo$rank <= 100, ]
    recommend.geo@data <- recommend.geo@data[!names(recommend.geo@data) %in% c('rank')]
    
    recommend.geo <- rbind(search.pt.geo, recommend.geo)
    
    idx <- recommend.geo@data %>%
      mutate(lnprice_guest = log(price_guest)) %>%
      select(bedrooms, guests_included, lnprice_guest) %>%
      sapply(scale) %>%
      dist(method = 'euclidean') %>%
      as.matrix() %>%
      melt(varnames = c('row', 'col')) %>%
      filter(value != 0.0 & col == 1) %>%
      arrange(value) %>%
      select(row)
    
    recommend.geo <- recommend.geo[idx$row,][1:10,]
    proj4string(recommend.geo) <- CRS(proj4string(hood.geo))
    
    rownames(recommend.geo@data) <- NULL
    recommend.geo$weight <- rev(as.integer(rownames(recommend.geo@data)))
    recommend.geo$text <- paste0('Room Type: ', recommend.geo$room_type,
                                 ' | # Bedrooms: ', recommend.geo$bedrooms,
                                 ' | # Guests Included: ', recommend.geo$guests_included,
                                 ' | Price: $', recommend.geo$price)
    
    recommend.geo
  })
  
  output$map <- renderLeaflet({
    tmap_leaflet(tm_shape(recommend.geo()) + 
                   tm_dots(col = 'property_type', size = 'weight', alpha = 0.9, palette = 'Dark2', 
                           title = 'Property Type', id = 'text') + 
                   tm_basemap('Esri.WorldTopoMap') + 
                   tm_layout(title = 'Recommended Airbnb Listings'))
  })
  
  output$recdf <- renderDataTable({
    datatable(recommend.geo()@data[c('neighbourhood_cleansed', 'property_type', 'room_type', 'bedrooms',
                                     'bathrooms', 'guests_included', 'price', 'listing_url')],
              colnames = c('Neighbourhood', 'Property Type', 'Room Type', '# of Bedrooms', 
                           '# of Bathrooms', '# of Guests Included', 'Rate per Night', 'Listing URL'),
              escape = FALSE)
  })
}


shinyApp(ui = recommend.ui, server = recommend.server, options = list(height = 1000))
```
